---
title: "ESM 206 Lab 5"
author: "Emily Hardison"
date: "10/29/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##### Lab 5 Objectives
- Learn how to parse dates with 'lubridate'
-Get counts of observations with count
- Uncount Rows
-ONe and two sample T-test
-Create a heatmap with geom_tile

```{r, include = FALSE}
library(tidyverse)
library(janitor)
library(lubridate)

lobster_abundance <- read_csv(here::here("data", "lobster_abundance.csv"), na = "-99999") %>% 
  janitor::clean_names()
  
  
```

Use the tidyr::uncount() function to convret the lobster data from frequency format to case format

```{r}
lobster_tidy <- lobster_abundance %>% 
  tidyr::uncount(lobster_count) # This function will make it so that every individual lobster has it's own count column 
```

#### Exploratory Data Visualization

We are only going to consider site as our variable of interest

```{r}
ggplot(data = lobster_tidy, aes(x = site, y = size_mm))+
  geom_jitter(aes(color = site), alpha=0.5)

# histogram

ggplot(data = lobster_tidy, aes(x = size_mm))+
  geom_histogram(aes(fill = site))+
  facet_wrap(~site, scales = "free")

# qqplot

ggplot(data = lobster_tidy, aes(sample = size_mm))+
  geom_qq()+
  facet_wrap(~site, scales = "free")


```

Overall, you are looking for a linear relationship on the qq plot to determine that it is "normal". Remember to group by your treatment groups when determining the distribution.

